---
title: "QuickTourQuiz"
author: "don-E Merson"
date: "October 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Quiz Questions for Module 1

https://quizlet.com/236833225/it-summit-2017-r-for-excel-users-module-1-r-studio-basics-flash-cards/

- How do you create a new project?	
- What is the console?	
- How do you print a sentence in R?	
- How do you create a source file in R?	
- What are the techniques to run a line of code in the R source file view?	
- What is a package?	
- What the different ways to install a package in R?	
- What is a variable?	
- What two conventions can you use for setting a variable?	
- Where can you see what variables you have created?	
- How do you create a list in R?	
- How do access the first element of a list?	
- How do access multiple sequential items in a list?	
- How do access non-sequential items in a list?	
- What does the [1] mean after you run "print("one thing")?
```{r}
print("one thing")
```

- What is type in programming?	
- How can you find the type of a variable in R? (2 ways)	
- What are a few different types in R?	
- How do you run a demo to show all the various types built into R?	
- How do you clear all your variables?	
- How do you load a package?	
- What things can you do in the R Studio Viewer?	
- How can use help from the command line?	
- How do you search help in R?	
- How do you view your history in R?	
- What items don't show up in your history?	
- What are the cheat sheets built into R Studio?	
- How do you access the Global and Project options?	
- How do you comment out a line in R?	
- How do you get and set your working directory?
 
