---
title: "Quick Tour -Part Two"
author: "don-E Merson"
date: "October 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Goals-Quick Tour (cont)
- Using variables
- What is shown in the environment tab
- What are common types in R
- How to create a function
- Viewer
- Help
- Options


# Variables
A variable is a container where you can store some type of value, function, or data
You can set them by variableName =“Value”
Or variableName <- “Value”
The second is more common in R
Try to use second form as sometimes first form doesn’t work
#Environment
Type in console
#List variables
#Type
This creates -> 
```{r}
hello ="test"

```

Type and Run the following
Vector victor
The [1] means it is the first of a vector
For vector think row in Excel
This is a row of 3 items in 1 column
#Types
- Types defined what operations can be used on data in a variable
- Numbers have operations like add, subtract,…
- Dataframes have operations like filtering and sorting
- Can use typeof command
Time to explore
Environment filled up
Clear it out
Let’s look at car package
View(Davis)
#Help
```{r}
help("cars")

```

Type 
#Search Help
#History
You can use up-arrow on keyboard to get previous values 
#Cheat Sheets

Global Options
Project Options
Code Menu
Comment in R is #
#Session and Working Directory
```{r}
getwd()
#setwd("C:/Repps/Itsummitrexcel/")

```

getwd()

